%\section{Sample Selection}

All of the objects discussed in this paper were observed with the NASA Infra-Red Telescope Facility (IRTF) and the SpeX instrument \cite{Rayner_1998} in the short-wavelength cross-dispersed mode (SXD), with a resolution of 2000.  During observations, we collected two distinct types of data.  One set before Spex was updated and another after.  The most recent upgrade to Spex occurred in August 2014.  This upgrade increased the observable wavelength.  See Table \ref{tab:maintab} for comparison.

%[HOW DO I PROPERLY CITE WAVELENGTH RANGE IN TABEL]\cite{RAYER_SPEX_OBSERVING_MANUAL_or_Spextool_2015_manual}.\\

Calibration frames, flats and arcs, were taken immediately after collecting data on a particular science object.  The final step was to obtain the remaining calibration data, pertaining to a particular A0.  Which standard to observe was determined by location and airmass.  For our purposes, an ideal A0V would deviate from the science objects' airmass by no more than 0.15 and be located in the same region of the sky as the science object.  This ensured minimal atmospheric derivations between our science and A0 stars.



Compairison of the data taken on each A0V standard to that of a well known A0, Vega, allowed for the determination of atmospheric residuals.  Using Spextool made data reduction, in this manner, possible.  The difference between an observed A0 and the model for Vega can be attributed to atmospheric conditions existing at the time of observation.  The same atmospheric disturbances apply to all objects observed at the same time and airmass.  Telluric corrections can now be applied to the spectra of each science object.  During observations, integration times were altered as to maximize the Signal to Noise ratio (S/N). \cite{Cushing_2004}\\