\subsection{Sample Selection}


%Any stellar atlas needs to be comprehensive.
To better classify young stars ($\sim$11~Myr old), 
the most essential restriction on this atlas was to 
have each star be approximately the same age. 
%This database was built to better classify young stars ($\sim$11~Myr old), making it essential to restrict this atlas to stars of approximately the same age. 
%To better classify young stars ($\sim$11~Myr old), the more essential restriction on this atlas was that all the stars were approximately the same age.
Star forming regions are ideal locations for such stars, 
solidifying the choice of observing upperSco members.  
Surveying the literature verified all targets as members of this 
region.  In order to be build a comprehensive atlas of young 
stars, various spectral types needed to be included 
(from class M to class O).
%~[HOW DO WE KNOW THESE ARE UPPERSCO MEMBERS (DO A LIT SEARCH)]\\



%~[NEED TO ASK JESSICA, HOW THEY DETERMINED WHAT STARS WERE BINARY & WHICH HAD DISKS]\\

Prior to observation, each target star was properly vetted. 
Stars identified to have binary companions~\cite{binary_guy} or accretion 
disks~\cite{binary_guy}, were immediately eliminated from the target list.  
Restricting target objects based on such criteria ensures each observed 
spectra was as isolated and representative as possible.



%[HOW WERE PREVIOUS CLASSES DETERMINED (CONFIRM OPTICAL)]\\
To select potential targets, previously established spectral classes 
were used.  
%These classifications were made at optical wavelengths.
Sifting through catalogs in the literature uncovered established 
spectral classes, at optical wavelengths.    
References for each previous spectral classification 
can be found in Table~\ref{tab:maintab}.\\





%In ensure chosen targets span the necessary spectral class range, 
%previously established spectral classes were used.  The referenced 
%spectral classes were determined using optical observations.
%%To select potential targets, previously established spectral classes were used.  
%References for each stars optical classification 
%can be found in Table~\ref{tab:maintab}.\\
%~[INCLUDE HISTOGRAM OF N_STARS VS SPT TYPE]







